### 2012-10-21 doc/ops/report.tex
Made lots of changes and fixed some silly language

In academic research, there are a huge abundance of scientific papers available for
consumption for any given scientific pursuit. In 2010, the famous journal,
PLOS One (\url{http://plosone.org}), reached the 10,000 papers published milestone \cite{PlosOne2010}. If you 
are doing background reading for a paper you are authoring, or looking for 
research on a specific topic that interests you, the vast quantity of data available can often be
quite daunting and choosing which papers to read very difficult. This problem
is further exacerbated when there is a time limit on the research to be carried
out. Partridge aims to aid the reader in finding documents relative to their
interests through the use of Artificial Intelligence techniques.

\section{Work to be tackled}

The main body of work to be tackled during the project is the Natural Language
Parsing (NLP) element of the application.

\section{Project Deliverables}

\bibliographystyle{IEEEannot}
\nocite{*}
\bibliography{report}

>>>>

For scholars carrying out a literature review or researching a specific topic
the vast quantity of research papers available on the internet can often be quite daunting;  
with the advent of the `Information Age', choosing which papers to read 
has become very difficult. This problem is exacerbated when there is a 
time limit to the research. Partridge aims to aid the 
reader in finding documents aposite to their interests through the use of 
Artificial Intelligence techniques. As well as making research processes 
more efficient and saving time, the program may also help the scholar to find
papers that they may otherwise not have read.

Partridge will use a web interface to allow users to specify particular
research topics. This can be done through manual entry of interests and types of 
report or by allowing the application to collate the papers that the user 
has read and to learn what is relevant to them. By appropriating this information,
Partridge will use learning algorithms to examine and classify the available
corpus of literature and make recommendations as to which articles the
scholar would find most helpful.

\section{Work to be `tackled':}
Despite the need for a web interface, the main body of the work in this project 
comes from the backend of the system and the Artificial Intelligence that drives it.

Initial research must be undertaken  into Natural Language
Parsing techniques and how different features of a text can be used to
classify papers. Furthermore, clear identification of the attributes which
allow the system to understand the differences between texts is vital.

Once these features are understood, a learning algorithm will be developed to
analyse scientific papers and to store information about the differences between 
them. The system will make use of some third party software (SAPIENTA) to help
with this process. Additionally, knowledge from CS36110 Machine will be used in
this project.

The first iteration of the system should the search for  that match specific criteria,
corresponding directly to `features' identified using the aforementioned AI
algorithms. Further iterations could be used  to build a profile based upon the user's 
reading history and used to make suggestions for further.

\section{`Project Deliverables'}

Although a formal 'XP' methodology will not be adopted since this is an
individual project, the project will be developed using an agile approach. It will be built in an
iterative manner. An initial release of the product will be made as soon as
possible. Subsequent releases will be made in iterations of two months.

Deliverables include:
\begin{itemize}
    \item Initial version of the system with restricted functionality; This
    would  use simple search and filtering techniques to find relevant research
    papers;
    \item Progress report evaluating the initial product and outlining ongoing
    development of the Artificial Intellegince underlying the results
    classifier module;
    \item Release two of the product, including result classifying behaviour;
    \item Demonstration of the artificial intelligence in the product;
    \item Following iteration three, the next release of the product will show
    evolved classification behaviour.
    \item Final report and release of software.
\end{itemize}

\renewcommand{\refname}{Initial Bibliography} 
\bibliographystyle{plain}
\nocite{*}
\bibliography{report}
